---
title: "Introduction to WebMaps"
subtitle: "Lesson 4: Leaflet maps with R"
author: "Dr. **Cyrille Médard de Chardon**"
institute: "<br>University of Luxembourg &<br>Luxembourg Institute of Socio-Economic Research (LISER)"
date: "<br>April 1, 2022"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, custom/custom.css] #xaringan-themer.css
    #css: [default, xaringen-themer.css, custom.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: false
      beforeInit: "custom/macros.js"
      
# Resources used to generate this presentation
#remotes::install_github("yihui/xaringan")
#https://slides.yihui.org/xaringan/

#devtools::install_github("gadenbuie/xaringanExtra")
#https://github.com/gadenbuie/xaringanExtra

#install.packages("xaringanthemer")
#https://github.com/gadenbuie/xaringanthemer

# formatting information
# https://bookdown.org/yihui/rmarkdown/xaringan-format.html#content-classes

---
class: 
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(xaringanthemer)
```

```{r xaringanExtra, echo=FALSE}
xaringanExtra::use_xaringan_extra(c("tile_view", "animate_css"))
```

# Lesson 3

.pl[
## Agenda
- Making a Leaflet WebMap with R
- Custom base maps
]

.pr[
## Homework reminder

Class activities, homework, and assignments are due next week by the end of the day on May 19th (Thursday).

]

---
# Create a Leaflet WebMap with R

.pull-left[
We will quickly demonstrate how you can create a WebMap with the R KnitR package.

Create a new Rstudio project and add the `RLeaflet.Rmd` document to it, then open it in RStudio.

You will likely need to install the KnitR, and Rgdal packages - do so.

This file is a mark-down file (the same used to create this lesson content) that allows the easy styling of text into HTML. The `R` component allows the blending of R code with HTML (or PDF and other formats). This allows you to embed a narrative for your map very easily.

To test the code simply click the `Knit` button in the toolbar above your code.

This will create an HTML file in the same location as your Rmd file.
]

.pr[
You can see the full [documentation for making WebMaps with Leaflet in R](https://rstudio.github.io/leaflet/).

The code is relatively simple and requires many of the same inputs as done using JS.

.ts[
```{R, eval=FALSE}
leaflet(width='100%') %>% 
  setView(lng=lux_lng,lat=lux_lat, zoom=9) %>% 
  addTiles() %>% 
  addMarkers(lng=points_lng, lat=points_lat, popup=popup_content)
```
]
]

---
class: inverse, center, middle, activity
# Activity 1: Create a WebMap using the R Leaflet package

.pl[
See the [resources](rsrcs/l4/lesson4.zip) for this week.

Have Knitr build the WebMap for you.

Add it to your website.
]

---
# Using a Mapbox base map

.pull-left[
## Get your Mapbox token
To get your base Mapbox map token:
- Go to [MapBox](https://www.mapbox.com/) and create an account.
- Go to your account to copy your token.
  - It should look like **pk.eyJ1Ij...yeGwQRd4m8r9mQQ**

### Like in Lesson 2
Following the [Leaflet quick-start instructions](https://leafletjs.com/examples/quick-start/#setting-up-the-map) and add your key at the line:
```{js}
accessToken: 'your.mapbox.access.token'
```

Remember that I provided WebMap templates in the lesson 2 [resources](rsrcs/l4/lesson4.zip).

]

.pr[
## Creating your own map style
You can customize your own map style if you would like.
- Go to [Mapbox Studio](https://studio.mapbox.com/) under the Products heading.

We will not cover that here, but be aware of it.
]

---
# Adding and styling multiple data sources

.pull-left[

**It's possible to add multiple data sets**

Just create the styles:
.ts[
```{js}
let line_style = {
    "color": "black",
    "dashArray": "4 4",
    "weight": 2
            };

let tunnel_style = {
    "color": "black", 
    "weight": 4
            };
```
]

Then retrieve the data.
]

.pull-right[
.ts[
```{js}
fetch("lines.geojson")
    .then(function(response) { return response.json(); })
    .then(function(data) {
        L.geoJSON(data, {style: line_style}).addTo(map);
});

fetch("stations.geojson")
    .then(function(response) { return response.json(); })
    .then(function(data) {
        L.geoJSON(data, {
            pointToLayer: function(point, latlng) {
                return L.marker(latlng);
                //return L.circle(latlng, 1000);
            },
            onEachFeature: function(feature, layer) {
                layer.bindPopup(feature.properties.NOM_GARE);
            }
        })
        .addTo(map);
});

fetch("tunnels.geojson")
    .then(function(response) { return response.json(); })
    .then(function(data) {
        L.geoJSON(data, {style: tunnel_style}).addTo(map);
});
```
]
]
 
---
class: inverse, center, middle, activity
# Activity 2: Create a CFL WebMap using Mapbox

.pull-left[
See the [resources](rsrcs/l4/lesson4.zip) for this week.

Use the CFL GeoJSON data to display Luxembourg's:
- Train lines
- Train stations
- Train tunnels

Use the Mapbox basemap:
- Update the tileLayer source `L.tileLayer(MAPBOX_TILE_URL, {...})`
- Update the token `accessToken: YOUR_TOKEN`
- Update the map id `id: 'mapbox/streets-v11'`
]

.pr[
The easiest option is to use the [async method](Lesson3.html) for loading multiple GeoJSON data sets to your WebMap.

**Remember this will only function when on your server**

See the previous slides for additional information.
]

---
class: inverse, center, middle, activity
# Homework and final assignment

---
# Final homework assignments WebMap

Your **final homework assignment** is due by the **end of the day on May 19th/Thursday**.

Like previous lessons your homework is to complete all activities but also reproduce what you have learned but using independent data and ideas.

.pl[

## R map
You must create **another** Leaflet WebMap in R with data and theme of your choice.
]

.pull-right[
## Leaflet full feature map
You will create a WebMap of a topic of your choice.
You will create a Leaflet map that contains:
- A Mapbox basemap (of your choice)
- A legend
- An interactive info box
- A context for the map - what's the purpose of the map? The story?
- This map is worth about a **quarter** of your WebMap course-section grade
]

---

# Homework

Your **final homework assignment** is due by the **end of the day on May 19th/Thursday**.

.pl[
## Exercises
Finish the exercises from today's lecture.
- Add to your **sync** map the:
  - legend and
  - info box
- Create the leaflet map in R
- Create the WebMap with a Mapbox base map and token 
]

.pull-right[
## Replication
- Create an additional Leaflet WebMap using data and theme from outside this course in R
- Final assignment map (previous slide)
]

### **Like all previous lessons, only homework [on the server](http://167.99.221.7/) is evaluated.**

Make sure that your index page links to your individual WebMaps correctly so that they can be found.

