---
title: "Introduction to WebMaps"
subtitle: "Lesson 3: Legendary - Adding functionality"
author: "Dr. **Cyrille Médard de Chardon**"
institute: "<br>University of Luxembourg &<br>Luxembourg Institute of Socio-Economic Research (LISER)"
date: "<br>April 1, 2022"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, custom/custom.css] #xaringan-themer.css
    #css: [default, xaringen-themer.css, custom.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: false
      beforeInit: "custom/macros.js"
      
# Resources used to generate this presentation
#remotes::install_github("yihui/xaringan")
#https://slides.yihui.org/xaringan/

#devtools::install_github("gadenbuie/xaringanExtra")
#https://github.com/gadenbuie/xaringanExtra

#install.packages("xaringanthemer")
#https://github.com/gadenbuie/xaringanthemer

# formatting information
# https://bookdown.org/yihui/rmarkdown/xaringan-format.html#content-classes

---
class: 
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(xaringanthemer)
```

```{r xaringanExtra, echo=FALSE}
xaringanExtra::use_xaringan_extra(c("tile_view", "animate_css"))
```

# Lesson 3

.pl[
## Agenda
- Debugging a WebMap
- Adding external data
- Creating a legend
- Creating an interactive information panel
]

.pr[
## Homework reminder

Homework is due before the next class.
So today's lesson work and homework is due next week.

]

---
# Adding external data

.pl[
We can add various data types to a Leaflet map.

- GeoJSON data
  - Transforming GeoJSON to JS
  - Loading GeoJSON

]

---
# Adding a legend

---
# Adding an interactive information panel


---

class: inverse, center, middle, activity
# Section/activity divider

.tl[
larger text

]

---

